Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-11-01 Article/main.tex
Article Finished

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.

@@

\begin{itemize}
\item
Games that would involve some form of sorting and matching are ideal for teaching declarative knowledge.
\item
Conceptual knowledge is beast taught through demonstrations and once again a sorting type game where the sorting is based on the common trait of the content or topic.
\item
A demonstration that displays the failure of not complying with the rules is helpful for a topic under the rules-based knowledge domain.
\item
Procedural knowledge is best taught through having the learners work through the procedure itself in some means.
\item
Soft Skills are best taught through having the learner repeatedly apply the skill in question u=in various scenarios.
\item
Immersing the learner within a phenomena found in the affective knowledge domain is an effective means of teaching them about it.
\item
Kapp\cite{Kapp2012a} states that observation is an ideal method of teaching the learner about a topic in the psychomotor domain.
\end{itemize}

@@

\begin{table}[h]
\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
\begin{adjustwidth}{-0.5cm}{}
\begin{tabular}{|c|c|c|c|}
\hline

@@

\section{Synthesis from Research}
From the literature and case studies examined, there are several key qualities that they share among each other either under the same descriptor or with similar descriptions with different names. It is these qualities that will form the basis to answer the question posed in the beginning of this study.
\\\\
The first quality is shared amongst Merrill's First Principles\cite{Merrill2002} and two of the case studies\cite{Dincelli2020,Sheng2007}. \textit{Reflection} is then a vital quality to a serious game if intended to be used in an educational environment and is described as giving a user some time after being presented with new knowledge or a task to dwell on what they have experienced.
\\\\
The second quality a serious game should make use of is that of \textit{Feedback}. All of the case studies\cite{Dincelli2020,Sheng2007,allers2021children} mention as such and Merrill\cite{Merrill2002} refers to it under the diminishing coaching corollary. A user should be presented with feedback on how they are progressing on a given set of tasks within the game at some point and as they progress the amount of feedback should be slowly diminished. The feedback amount should also be tied to the performance of the user - increasing if they begin to struggle and decrease if not. Since feedback can take on many different forms, the type of feedback as well as the method of delivery is dependant on the topic being taught.
\\\\
Another quality that should be implemented is that the serious game should showcase and teach topics through the use of \textit{Story-telling}. The case studies\cite{Dincelli2020,Sheng2007,allers2021children} all mention the use of this and John Keller's ARCS model\cite{keller1987development}, specifically under the attention element, also states that this is a proponent of keeping users engaged. A game should then allow for a story to take place during the teaching of a topic which can also be done in several ways - such as contextually with Anti-phishing phil or as the main focus of the topic as with the SETA artefact\cite{Dincelli2020} and Happy Hippo\cite{allers2021children}. Another means to accomplish this is to make use of an agent that guides the user through the game. 
\\\\

\subsection{Recommendations per Knowledge Domain}

\section{Limitations and Future Research}
This study made use of various fields of study as well as case studies of serious games and their design in order to answer the question posed. The current limitations of answering the question largely center around the amount of literature sourced. In terms of the fields looked at (pedagogy, ludology and gamification) these seem to be sufficient in terms of what literature can be used and as such it is the specific literature used that imposes limitations. There are many more instructional theories that could be considered and as such future research could delve into more theories and expand the knowledge base used to answer the question. Another limitation comes from the case studies used. All of the main case studies discussed in this article had a focus on computer security to varying degrees. Due to this, future research could include case studies on the design, implementation or development of serious games in other fields.
\\\\
Furthermore, a more practical approach to future research could include the development of a serious game on a topic based in one of the knowledge domains mentioned. This could include the development an artefact for user testing, similarly to Anti-phishing phil\cite{Sheng2007}, based off of the findings of this study or the designing of such an artefact more in line with the "Happy Hippo" game\cite{allers2021children}.

\section{Conclusion}
This study discussed the current state of the paradigms that instructional institutions are based off of and how society has progressed and developed different needs than the systems in place currently provide. As such, research into how serious games can be used in an educational environment was conducted with specific focus on the fields of pedagogy, ludology and gamification in order to answer the question, \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}. Through a literature review in these fields, various instructional theories were found that could be helpful to answer the question as they are able to be translated into the context of games relatively easy. Furthermore, several research papers were used as case studies to discover what design principles are typically followed in the development of serious games. This information was then used to identify what are the major qualities which a serious game should have in order to be effective in a educational environment as well as providing specific recommendations for various knowledge domains. The qualities identified were allowing for Reflection, providing Feedback, making use of Story elements and Structuring.

>>>>

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.

@@

\begin{itemize}
\item
Games that would involve some form of sorting and matching are ideal for teaching declarative knowledge.
\item
Conceptual knowledge is beast taught through demonstrations and once again a sorting type game where the sorting is based on the common trait of the content or topic.
\item
A demonstration that displays the failure of not complying with the rules is helpful for a topic under the rules-based knowledge domain.
\item
Procedural knowledge is best taught through having the learners work through the procedure itself in some means.
\item
Soft Skills are best taught through having the learner repeatedly apply the skill in question within various scenarios.
\item
Immersing the learner within a phenomena found in the affective knowledge domain is an effective means of teaching them about it.
\item
Kapp\cite{Kapp2012a} states that observation is an ideal method of teaching the learner about a topic in the psychomotor domain.
\end{itemize}

@@

\begin{table}[h]
\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
\begin{adjustwidth}{-0.6cm}{}
\begin{tabular}{|c|c|c|c|}
\hline

@@

\section{Synthesis from Research}
From the literature and case studies examined, there are several key qualities that they share among each other either under the same descriptor or with similar descriptions with different names. It is these qualities that will form the basis to answer the question posed in the beginning of this study.
The first quality is shared amongst Merrill's First Principles\cite{Merrill2002} and two of the case studies\cite{Dincelli2020,Sheng2007}. \textit{Reflection} is then a vital quality to a serious game if intended to be used in an educational environment and is described as giving a user some time after being presented with new knowledge or a task to dwell on what they have experienced.
The second quality a serious game should make use of is that of \textit{Feedback}. All of the case studies\cite{Dincelli2020,Sheng2007,allers2021children} mention as such and Merrill\cite{Merrill2002} refers to it under the diminishing coaching corollary. A user should be presented with feedback on how they are progressing on a given set of tasks within the game at some point and as they progress the amount of feedback should be slowly diminished. The feedback amount should also be tied to the performance of the user - increasing if they begin to struggle and decrease if not. Since feedback can take on many different forms, the type of feedback as well as the method of delivery is dependant on the topic being taught. As part of this quality, a serious game should also be designed to create an environment in which users are able to complete smaller tasks and are rewarded for these smaller successes - as per the ARCS model\cite{keller1987development}.
Another quality that should be implemented is that the serious game should showcase and teach topics through the use of \textit{Story-telling}. The case studies\cite{Dincelli2020,Sheng2007,allers2021children} all mention the use of this and John Keller's ARCS model\cite{keller1987development}, specifically under the attention element, also states that this is a proponent of keeping users engaged. A game should then allow for a story to take place during the teaching of a topic which can also be done in several ways - such as contextually with Anti-phishing phil or as the main focus of the topic as with the SETA artefact\cite{Dincelli2020} and Happy Hippo\cite{allers2021children}. Another means to accomplish this is to make use of an agent that guides the user through the game which can be used in accordance with the Learner Guidance corollary from Merrill's First Principles\cite{Merrill2002}. 
The last major quality a serious game should possess is that of \textit{Structuring}. This quality refers more to the content the game will deal with in terms of the instructions given as well as how the difficulty of problems could progress. It is derived from both Merrill's First Principles\cite{Merrill2002}, the ARCS model\cite{keller1987development} as well as the framework by Callaghan\cite{callaghan2018}. From the ARCS model\cite{keller1987development}, specifically Confidence, and Callaghan's\cite{callaghan2018} framework it is clear that a serious game should be structured with simple goals and clear expectations from the user and by structuring a game's instructions in this manner the user will be motivated to continue playing and therefore learning. Structuring the problems and tasks within the game should follow a similar method to how Feedback is provided - increasing the difficulty as a user gets them correct and lessening the difficulty when they are struggling to once again keep engagement with the game high. Merrill's First Principles\cite{Merrill2002} discusses this quality in several Principles and their subsequent corollaries - some of which refer to the difficulty scaling mentioned above. As such, a serious game's structure should be centred around the problems themselves - or the knowledge being taught when dealing with Affective knowledge and soft skills. The tasks given to a user should be both varied to keep the users' attention as well as be consistent in the ways the user interacts with them. This approach should keep users motivated to use the game according to the ARCS model\cite{keller1987development} as it makes use of both the Attention and Relevance elements.
While the remaining aspects of the pedagogical theories and design principles from the case studies are also useful in the implementation of a serious game, they are specific to the content being taught and as such should be considered in greater detail if a similar game to those were to be developed.

\subsection{Recommendations for Specific Knowledge Domains}
Kapp's\cite{Kapp2012a} recommendations are a helpful starting point to how to effectively teach content relating to the knowledge domains. 
\\\\
Referring back to Squire's\cite{Squire2003} descriptions of games as simulations - both Hi-fidelity and low fidelity. These types of serious games are certainly the most useful for teaching content found in the Affective, Soft Skills and Psychomotor domains since the best means to teach these is through immersing the user in the phenomena, repeated application of skills and observation respectively\cite{Kapp2012a}. Simulation-type serious games can also be used in the other domains such as with the game used to aid in teaching physics described by Deshpande and Huang\cite{Deshpande2011}. These types of games are also the most effective means for the psychomotor domain as shown by various studies\cite{Burke2009, Costanza2014, Ranalli2008, Tao2009}.
\\\\
The remaining knowledge domains tend to have some heavy overlap depending of the topic being covered. Sheng \textit{et al.}\cite{Sheng2007} discussed the Conceptual-Procedural principle in their game's development. To reiterate, it simply states that a topic cannot be fully understood from only the procedures or context - both are needed for a deeper understanding.

\section{Limitations and Future Research}
This study made use of various fields of study as well as case studies of serious games and their design in order to answer the question posed. The current limitations of answering the question largely center around the amount of literature sourced. In terms of the fields looked at (pedagogy, ludology and gamification) these seem to be sufficient in terms of what literature can be used and as such it is the specific literature used that imposes limitations. There are many more instructional theories that could be considered and as such future research could delve into more theories and expand the knowledge base used to answer the question. Future research could also include looking at various types of games and how they could teach content in the different knowledge domains to build upon Kapp's\cite{Kapp2012a} recommendations. Another limitation comes from the case studies used. All of the main case studies discussed in this article had a focus on computer security to varying degrees. Due to this, future research could include case studies on the design, implementation or development of serious games in other fields.
\\\\
Furthermore, a more practical approach to future research could include the development of a serious game on a topic based in one of the knowledge domains mentioned. This could include the development an artefact for user testing, similarly to Anti-phishing phil\cite{Sheng2007}, based off of the findings of this study or the designing of such an artefact more in line with the "Happy Hippo" game\cite{allers2021children}.

\section{Conclusion}
This study discussed the current state of the paradigms that instructional institutions are based off of and how society has progressed and developed different needs than the systems in place currently provide. As such, research into how serious games can be used in an educational environment was conducted with specific focus on the fields of pedagogy, ludology and gamification in order to answer the question, \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}. Through a literature review in these fields, various instructional theories were found that could be helpful to answer the question as they are able to be translated into the context of games relatively easy. Furthermore, several research papers were used as case studies to discover what design principles are typically followed in the development of serious games. This information was then used to identify what are the major qualities which a serious game should have in order to be effective in a educational environment as well as providing specific recommendations for various knowledge domains. The qualities identified were allowing for Reflection, providing Feedback, making use of Story elements and a well thought out Structuring of the game. Recommendations for the different knowledge domains were also given.
\\
\section*{Acknowledgements}
This article was part of a research project for an Honours degree and as such I would like to thank my supervisor, Günther Drevin, for their aid throughout the year as well as for the lessons on the field of ludology as well as the School of Computer Science and Information Systems at the North West University for providing this opportunity.
